We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-03 paper/paper.tex
some pagragraphs

The consensus is that these structures are hard to find in
simulations. 
Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from studying individual halos to pairs has been
motivated by the realization that

>>>>

The consensus is that these structures are hard to find in
simulations. 
Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from studying individual halos to pairs has been
motivated by the hypotesis hat the location of the Local Group in
the cosmic web should play a determinant role in building up planar
satellite distributions through preferential alignments and accretions
histories of galaxies.

To
